---
title: "ex2"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, message=FALSE}

# library for data wrangling

rm(list=ls()) # removes all objects in the current Environment
gc()
setwd("C:/Users/scasella/OneDrive - Seves Spa/EX2 Dataset")

library(data.table)
library(dplyr)
library(tidyverse)
library(hhi) # Herfindahl-Hirschman Index

# library for regression

library(haven)         # For loading data from Stata
library(broom)         # For showing models as data frames
library(fixest)        # For fast, nice, fixed effects regression
library(modelsummary)  # For side-by-side regression tables
library(rdrobust)
library(rddensity)
library(modelsummary)
library(stargazer)

knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
### load 3 datasets

load("sample.Rdata")
load("Financial.Rdata")
load("company2015.RData")
```

## Variable information from 2 datasets

<br> 
`sample.RData` - Patent Portfolio

Source : `OECD, REGPAT Database, March 2018` - is presenting patent data that have been linked to regions utilising the addresses of the applicants and inventors

| Variable                | Descriptions                                                      |
|-------------------------|-------------------------------------------------------------------|
| Patent_appln_id         | PATSTAT Application identifier                                    |
| Company_name            | Company name                                                      |
| Company_id              | Unique company identifier                                         |
| Patent_publn_nr         | Patent publication number                                         |
| Up_reg_code             |                                                                   | 
| Reg_code                | NUTS3 region code                                                 |
| Pub_nbr                 |                                                                   |
| Prio_year               | Priority year (filing year for a patent)                          |
| Ctry_code               | Country                                                           |
| ipc                     | International Patent Classification                               |
| Inv_name                | Inventor’s name                                                   |
| Address                 | Address                                                           |
| IPC4                    | List of International Patent Classification classes - 8th edition |


`Financial.RData` - Top corporate R&D Investors - Financial data of those company on sample.Rdata above

| Variable                | Descriptions                               |
|-------------------------|--------------------------------------------|
| Company_id              | Unique company identifier (from 1 - 2000)* |
| Year                    | 2011 - 2014                                |
| worldrank               | From 1 - 2000                              |
| rd                      | Research and Development investment (MEUR) | 
| ns                      | Net sales (MEUR)                           |
| capex                   | Capital expenditure (MEUR)                 |
| op                      | Operating profits (MEUR)                   |
| emp                     | Number of employees                        |

<br>



```{r}
### What is the firm portfolio ? 
## number of Patent each company / firm portfolio

dt <- unique(sample[,c("Company_name","Patent_appln_id")],by = c("Company_name","Patent_appln_id"))
dt <- dt %>% group_by(Company_name) %>% summarize(nb_pat = n())
NB_Pat <- dt[order(-dt$nb_pat),]
head(NB_Pat,66)
```

## Combining 2 datasets

- In the sample and Financial data sets, I'll create unique ID variables using the variables `Company_id` and `Prio_year`. 
- In the Financial data, I removed the data from year 2009 because data for this year is not present in the Sample data set. 
- I'll use the inner join method to join the rows matched by the newly created unique ID. 

```{r}

# create unique ID in both data sets to combine
sample <- sample %>%
  mutate(Company_id = as.character(Company_id)) %>%
  unite(Id_column, Company_id, Prio_year, sep = "_", remove = FALSE, na.rm = FALSE)

Financial <- Financial %>%
  #mutate(Company_id = as.character(Company_id)) %>%
  filter((is.na(Year) | Year != 2009)) %>%
  inner_join(company2015, by = c("Company_id" = "Company_id")) %>%
  unite(Id_column, Company_id, Year, sep = "_", remove = FALSE, na.rm = FALSE)

## Inner join both data sets
dt <- Financial %>%
  inner_join(sample %>%
               select(-Company_id, -Company_name, -Ctry_code),
             by = c("Id_column" = "Id_column"))
  

dim(dt)  # dim is the function to returns the dimension like number of rows and columns
```
### Technological Diversification

```{r}

# herf function
herf <- function(x){
    sum(x^2)
}

# Technological diversification
TD <- dt %>%
  select(Patent_appln_id, Company_name, Prio_year, IPC4) %>%
  group_by(Company_name, Prio_year, Patent_appln_id, IPC4) %>%
  distinct(IPC4, .keep_all = TRUE) %>%
  group_by(Company_name, IPC4, Prio_year) %>%
  summarise(Ni = n()) %>%
  group_by(Company_name, Prio_year) %>%
  summarise(pat = sum(Ni, na.rm = TRUE),pj = Ni/sum(Ni)) %>%
  mutate(`Technological_diversification` = herf(pj)) %>%
  distinct(`Technological_diversification`, .keep_all = TRUE) %>%
  unite(Id_column, Company_name, Prio_year, sep = "_", remove = FALSE, na.rm = FALSE) %>% # ID variable to merging the data later
  select(-pat, -pj)

TD
```

### Absorptive Capacity

```{r}
AC <- dt %>%
  group_by(Company_name, Prio_year) %>%
  summarise(rd = mean(rd), ns = mean(ns)) %>%
  mutate(`Absorptive_Capacity` = rd/ns) %>%
  unite(Id_column, Company_name, Prio_year, sep = "_", remove = FALSE, na.rm = FALSE) %>% # ID variable to merging the data later
  select(-rd, -ns)

AC
```

### Innovation Performance (Patent Value)

```{r}
IP <-dt %>%
  distinct(Company_name, Prio_year, Patent_appln_id) %>%
  group_by(Company_name, Prio_year) %>%
  summarise(`Innovation_Performance` = n()) %>%
  unite(Id_column, Company_name, Prio_year, sep = "_", remove = FALSE, na.rm = FALSE) # ID variable to merging the data later

IP
```

## Environmental Dynamism
```{r}
ED <- dt %>%
  #distinct(Company_name, Prio_year, NACE2) %>%
  group_by(Company_name, Prio_year, NACE2) %>%
  summarise(Environmental_Dynamism = mean(rd)) %>%
  unite(Id_column, Company_name, Prio_year, sep = "_", remove = FALSE, na.rm = FALSE) # ID variable to merging the data later

ED
```

## Count of location
```{r}
locations <- dt %>%
  group_by(Company_name, Prio_year, Ctry_code) %>%
  summarise(Locations = n()) %>%
  unite(Id_column, Company_name, Prio_year, sep = "_", remove = FALSE, na.rm = FALSE) # ID variable to merging the data later

locations
```



## Merging calculated variables in one dataset

```{r}
data <- TD %>%
  inner_join(AC %>%
               ungroup() %>%
               select(-Company_name, -Prio_year), 
             by = c("Id_column" = "Id_column")) %>%
  inner_join(IP %>%
               ungroup() %>%
               select(-Company_name, -Prio_year),
             by = c("Id_column" = "Id_column")) %>%
  inner_join(ED %>%
               ungroup() %>%
               select(-Company_name, -Prio_year, -NACE2),
             by = c("Id_column" = "Id_column")) %>%
  inner_join(locations %>%
               ungroup() %>%
               select(-Company_name, -Prio_year, -Ctry_code),
             by = c("Id_column" = "Id_column")) %>%
  relocate(Company_name, Prio_year)

data
```
```{r}
stargazer(as.data.frame(data), type = "text",
          header = FALSE,
          single.row = FALSE)

```


### Regression (with taking logs)

```{r}
# TD and IP relationship
m1 <- lm(log(Innovation_Performance + 1) ~ log(Technological_diversification + 1) + log(Locations) + factor(Prio_year) + factor(Company_name), data = data)

#quadratic model
m2 <- lm(log(Innovation_Performance + 1) ~ I(log(Technological_diversification + 1)^2) + log(Locations) + factor(Prio_year) + factor(Company_name) , data = data)

# with year and company dummies
m3 <- lm(log(Innovation_Performance + 1) ~ log(Technological_diversification + 1) + Absorptive_Capacity + Environmental_Dynamism + log(Locations) + factor(Prio_year) + factor(Company_name), data = data)

# TD X AC 
m4 <- lm(log(Innovation_Performance + 1) ~ log(Technological_diversification + 1) * Absorptive_Capacity + Absorptive_Capacity + log(Locations) + factor(Prio_year) + factor(Company_name), data = data)

# TD X AC  without control variable
m5 <- lm(log(Innovation_Performance + 1) ~ log(Technological_diversification + 1) * Absorptive_Capacity + Absorptive_Capacity, data = data)

# TD X ED
m6 <- lm(log(Innovation_Performance + 1) ~ log(Technological_diversification + 1) * Environmental_Dynamism + Environmental_Dynamism + log(Locations) + factor(Prio_year) + factor(Company_name), data = data)

# TD X ED without control variable
m7 <- lm(log(Innovation_Performance + 1) ~ log(Technological_diversification + 1) * Environmental_Dynamism + Environmental_Dynamism, data = data)

# TD X Locations
m8 <- lm(log(Innovation_Performance + 1) ~ log(Technological_diversification + 1) * Locations + Absorptive_Capacity + Environmental_Dynamism + log(Locations) + factor(Prio_year) + factor(Company_name), data = data)


stargazer(m1, m2, m3, m4, m5,m6,m7,m8, type = "text")

```







